---
title: "211109 nervousness additional analyses"
author: "Anne Margit"
date: "11/05/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, results = "hide"}
load("data_analyse2_p1.Rdata")
load("data_analyse2_p2.Rdata")
load("data_analyse2_p3.Rdata")
```

```{r, message=F}
options(scipen=999)

library(dplyr)
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(rockchalk)
library(effects)
library(nlme)
library(lattice)
library(broom.mixed)
library(purrr)
library(stargazer)
library(viridis)  
```


```{r, message=F, comment=NA}
data_analyse2_p1$Edu <- as.numeric(data_analyse2_p1$Edu)

```

# Phase 1
*Random: IC for ID and Country + Covariates Gender and Education*
```{r, message=F, comment=NA}
model_Nervp1 <- lme(fixed = Nerv ~ Gender + Edu + Age_new,
                  random = ~1 | Country/ID, 
                  data = data_analyse2_p1, 
                  na.action = na.omit)

summary(model_Nervp1)
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_Nervp1 <- effect("Age_new", model_Nervp1)

plot_Nervp1 <- ggplot(as.data.frame(ef_Nervp1), 
  aes(Age_new, fit, color=Age_new)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_minimal(base_size=12) + 
  labs(title="Nervousness during tightening of restrictions", y = "Nervousness") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(name ="Age", labels=c("18-24", "25-44", "45-64", "65+")) +
  theme(legend.position = "none") +                 
  scale_color_discrete() + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_Nervp1
```

```{r, message=F, comment=NA}
intervals(model_Nervp1)
VarCorr(model_Nervp1)
```

*Effect sizes*
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p1 %>% 
  group_by(ID) %>%
  summarize_at(c("Nerv"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("Nerv"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect size = regression coefficient / average ISD of Nervousness

```{r, message=F, comment=NA}
coef_Nervp1 = tidy(model_Nervp1, 
               effects = "fixed")

coef_Nervp1 <- coef_Nervp1 %>%
  mutate (e_size = estimate/0.6072834) %>% 
  mutate(across(2:7, round, 2)) 
         
```

```{r}
coef_Nervp1
coef_Nervp1 <- as.matrix(coef_Nervp1)
```

# Phase 2

*Best model*

> Random intercept for ID and Country, random slope for Country and ID, no correlation between random intercept and slope for Country, AR correlation structure at Measurement level

```{r, message=F, comment=NA}
data_analyse2_p2$Edu <- as.numeric(data_analyse2_p2$Edu)

data_analyse2_p2 <- data_analyse2_p2[with(data_analyse2_p2, order(Country, ID, Time)),]
data_analyse2_p2$Time <- as.numeric(data_analyse2_p2$Time)

model_Nervp2 <- lme(fixed = Nerv ~ Gender + Edu + DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = list(Country = pdDiag(~DaysMax_p2), ID = ~DaysMax_p2),  
                  data = data_analyse2_p2, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))
summary(model_Nervp2)

```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_Nervp2 <- effect("DaysMax_p2:Age_new", model_Nervp2)
plot_Nervp2 <- ggplot(as.data.frame(ef_Nervp2), aes(DaysMax_p2, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=12) + 
  labs(title="A",
       x="Days", y = "Nervousness") +
  xlim(0,80)+
  theme(plot.title = element_text(size=12)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_Nervp2
```

```{r, message=F, comment=NA}
VarCorr(model_Nervp2)
intervals(model_Nervp2, which = 'fixed')
```

*Effect sizes*

**Within person SD and average within person SD**

```{r, message=F, comment=NA}
ISDs <- data_analyse2_p2 %>% 
  group_by(ID) %>%
  summarize_at(c("DaysMax_p2", "Nerv"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("DaysMax_p2", "Nerv"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect sizes for intercept and main effect of age and covariates = regression coefficient / average ISD of Nervousness
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of Nervousness
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of Nervousness
> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of Nervousness over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_Nervp2 = tidy(model_Nervp2, 
               effects = "fixed")
coef_Nervp2 <- coef_Nervp2 %>%
  mutate(e_size = ifelse(row_number()== 1 | row_number()== 2 |  row_number()== 3 |  row_number()== 5 |  row_number()== 6 |  row_number()== 7, estimate/0.588966, (estimate*28)/0.588966)) %>%
  mutate(across(2:7, round, 2)) 
          
```

```{r}
coef_Nervp2 <- as.matrix(coef_Nervp2)
coef_Nervp2
```

# Phase 3

> Random intercept for ID and Country, random slope for ID and AR correlation structure at Measurement level

```{r, message=F, comment=NA}
data_analyse2_p3$Edu <- as.numeric(data_analyse2_p3$Edu)
data_analyse2_p3 <- data_analyse2_p3[with(data_analyse2_p3, order(Country, ID, Time)),]
data_analyse2_p3$Time <- as.numeric(data_analyse2_p3$Time)
model_Nervp3 <- lme(fixed = Nerv ~ Gender + Edu + DaysPhase3 + Age_new + DaysPhase3*Age_new,
                  random = list (Country = ~1, ID = ~DaysPhase3), 
                  data = data_analyse2_p3, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))
summary(model_Nervp3)
VarCorr(model_Nervp3)
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_Nervp3, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_Nervp3 <- effect("DaysPhase3:Age_new", model_Nervp3)
plot_Nervp3 <- ggplot(as.data.frame(ef_Nervp3), aes(DaysPhase3, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=12) + 
  xlim(0,80)+
  labs(title="B",
       x="Days", y = "Nervousness") +
  theme(plot.title = element_text(size = 12)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_Nervp3
```

```{r, message=F}
plot_Nervp2and3 <- ggarrange(plot_Nervp2, plot_Nervp3 , 
          ncol = 2, nrow = 1, common.legend=TRUE, legend= "bottom")
plot_Nervp2and3 <- annotate_figure(plot_Nervp2and3,top = text_grob("Nervousness trajectories during peak (A) and easing (B) of restrictions", size = 12))
```

```{r, message=F}
plot_Nervp2and3
```

*Effect sizes*
**Within person SD and average within person SD for Nervousness**
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p3 %>% 
  group_by(ID) %>%
  summarize_at(c("Nerv"), sd, na.rm=TRUE) %>%
  ungroup()
ISDs_av <- ISDs %>%
  summarize_at(c("Nerv"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect sizes for intercept and main effect of age = regression coefficient / average ISD of Nervousness
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of Nervousness
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of Nervousness
> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of Nervousness over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_Nervp3 = tidy(model_Nervp3, 
               effects = "fixed")
coef_Nervp3 <- coef_Nervp3 %>%
 mutate(e_size = ifelse(row_number()== 1 | row_number()== 2 |  row_number()== 3 |  row_number()== 5 |  row_number()== 6 |  row_number()== 7, estimate/0.5481823, (estimate*28)/0.5481823)) %>%
  mutate(across(2:7, round, 2)) 
```

```{r}
coef_Nervp3 <- as.matrix(coef_Nervp3)
coef_Nervp3
```

```{r}
stargazer(coef_Nervp1, coef_Nervp2, coef_Nervp3,
type="html", df = TRUE, out="star_coefNervp123.doc",  single.row=TRUE, digits = 2, align = TRUE)

stargazer(model_Nervp1, model_Nervp2, model_Nervp3,
type="html", df = TRUE, out="star_modelNervp123.doc",  single.row=TRUE, digits = 2, align = TRUE,
intercept.top = TRUE, intercept.bottom = FALSE)

```