---
title: "211109 inspired additional analyses"
author: "Anne Margit"
date: "11/05/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, results = "hide"}
load("data_analyse2_p1.Rdata")
load("data_analyse2_p2.Rdata")
load("data_analyse2_p3.Rdata")
```

```{r, message=F}
options(scipen=999)

library(dplyr)
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(rockchalk)
library(effects)
library(nlme)
library(lattice)
library(broom.mixed)
library(purrr)
library(stargazer)
library(viridis)  
```


```{r, message=F, comment=NA}
data_analyse2_p1$Edu <- as.numeric(data_analyse2_p1$Edu)

```

# Phase 1
*Random: IC for ID and Country + Covariates Gender and Education*
```{r, message=F, comment=NA}
model_Inspp1 <- lme(fixed = Insp ~ Gender + Edu + Age_new,
                  random = ~1 | Country/ID, 
                  data = data_analyse2_p1, 
                  na.action = na.omit)

summary(model_Inspp1)
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_Inspp1 <- effect("Age_new", model_Inspp1)

plot_Inspp1 <- ggplot(as.data.frame(ef_Inspp1), 
  aes(Age_new, fit, color=Age_new)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_minimal(base_size=12) + 
  labs(title="Inspiration during tightening of restrictions", y = "Inspiration") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(name ="Age", labels=c("18-24", "25-44", "45-64", "65+")) +
  theme(legend.position = "none") +                 
  scale_color_discrete() + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_Inspp1
```

```{r, message=F, comment=NA}
intervals(model_Inspp1)
VarCorr(model_Inspp1)
```

*Effect sizes*
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p1 %>% 
  group_by(ID) %>%
  summarize_at(c("Insp"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("Insp"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect size = regression coefficient / average ISD of Inspired

```{r, message=F, comment=NA}
coef_Inspp1 = tidy(model_Inspp1, 
               effects = "fixed")

coef_Inspp1 <- coef_Inspp1 %>%
  mutate (e_size = estimate/0.5828323) %>% 
  mutate(across(2:7, round, 2)) 
         
```

```{r}
coef_Inspp1
coef_Inspp1 <- as.matrix(coef_Inspp1)
```

# Phase 2

*Best model*

> Random intercept for ID and Country, random slope for ID, no correlation between IC and S for ID + AR correlation structure at Measurement level

```{r, message=F, comment=NA}
data_analyse2_p2$Edu <- as.numeric(data_analyse2_p2$Edu)
data_analyse2_p2 <- data_analyse2_p2[with(data_analyse2_p2, order(Country, ID, Time)),]
data_analyse2_p2$Time <- as.numeric(data_analyse2_p2$Time)
model_Inspp2 <- lme(fixed = Insp ~ Gender + Edu + DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = list(Country = ~1, ID = pdDiag(~DaysMax_p2)),
                  data = data_analyse2_p2, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~Time | Country/ID))
summary(model_Inspp2)
VarCorr(model_Inspp2)
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_Inspp2 <- effect("DaysMax_p2:Age_new", model_Inspp2)
plot_Inspp2 <- ggplot(as.data.frame(ef_Inspp2), aes(DaysMax_p2, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=12) + 
  labs(title="A",
       x="Days", y = "Inspiration") +
  xlim(0,80)+
  theme(plot.title = element_text(size=12)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_Inspp2
```

```{r, message=F, comment=NA}
VarCorr(model_Inspp2)
intervals(model_Inspp2, which = 'fixed')
```

*Effect sizes*

**Within person SD and average within person SD**

```{r, message=F, comment=NA}
ISDs <- data_analyse2_p2 %>% 
  group_by(ID) %>%
  summarize_at(c("DaysMax_p2", "Insp"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("DaysMax_p2", "Insp"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect sizes for intercept and main effect of age and covariates = regression coefficient / average ISD of Inspired
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of Inspired
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of Inspired
> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of Inspired over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_Inspp2 = tidy(model_Inspp2, 
               effects = "fixed")
coef_Inspp2 <- coef_Inspp2 %>%
  mutate(e_size = ifelse(row_number()== 1 | row_number()== 2 |  row_number()== 3 |  row_number()== 5 |  row_number()== 6 |  row_number()== 7, estimate/0.5925649, (estimate*28)/0.5925649)) %>%
  mutate(across(2:7, round, 2)) 
          
```

```{r}
coef_Inspp2 <- as.matrix(coef_Inspp2)
coef_Inspp2
```

# Phase 3

> Random: IC for ID and Country, S for ID, no correlation between IC and S for ID + AR

```{r, message=F, comment=NA}
data_analyse2_p3$Edu <- as.numeric(data_analyse2_p3$Edu)
data_analyse2_p3 <- data_analyse2_p3[with(data_analyse2_p3, order(Country, ID, Time)),]
data_analyse2_p3$Time <- as.numeric(data_analyse2_p3$Time)
model_Inspp3 <- lme(fixed = Insp ~ Gender + Edu + DaysPhase3 + Age_new + DaysPhase3*Age_new,
                  random = list (Country = ~1, ID = pdDiag(~DaysPhase3)), 
                  data = data_analyse2_p3, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))
summary(model_Inspp3)
VarCorr(model_Inspp3)
```


*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_Inspp3, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_Inspp3 <- effect("DaysPhase3:Age_new", model_Inspp3)
plot_Inspp3 <- ggplot(as.data.frame(ef_Inspp3), aes(DaysPhase3, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=12) + 
  xlim(0,80)+
  labs(title="B",
       x="Days", y = "Inspiration") +
  theme(plot.title = element_text(size = 12)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_Inspp3
```

```{r, message=F}
plot_Inspp2and3 <- ggarrange(plot_Inspp2, plot_Inspp3 , 
          ncol = 2, nrow = 1, common.legend=TRUE, legend= "bottom")
plot_Inspp2and3 <- annotate_figure(plot_Inspp2and3,top = text_grob("Inspiration during peak (A) and easing (B) of restrictions", size = 12))
```

```{r, message=F}
plot_Inspp2and3
```

*Effect sizes*
**Within person SD and average within person SD for Inspetic**
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p3 %>% 
  group_by(ID) %>%
  summarize_at(c("Insp"), sd, na.rm=TRUE) %>%
  ungroup()
ISDs_av <- ISDs %>%
  summarize_at(c("Insp"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect sizes for intercept and main effect of age = regression coefficient / average ISD of Inspired
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of Inspired
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of Inspired
> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of Inspired over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_Inspp3 = tidy(model_Inspp3, 
               effects = "fixed")
coef_Inspp3 <- coef_Inspp3 %>%
 mutate(e_size = ifelse(row_number()== 1 | row_number()== 2 |  row_number()== 3 |  row_number()== 5 |  row_number()== 6 |  row_number()== 7, estimate/0.5855497, (estimate*28)/0.5855497)) %>%
  mutate(across(2:7, round, 2)) 
```

```{r}
coef_Inspp3 <- as.matrix(coef_Inspp3)
coef_Inspp3
```

```{r}
stargazer(coef_Inspp1, coef_Inspp2, coef_Inspp3,
type="html", df = TRUE, out="star_coefInspp123.doc",  single.row=TRUE, digits = 2, align = TRUE)

stargazer(model_Inspp1, model_Inspp2, model_Inspp3,
type="html", df = TRUE, out="star_modelInspp123.doc",  single.row=TRUE, digits = 2, align = TRUE,
intercept.top = TRUE, intercept.bottom = FALSE)

```